Optimal Task Phasing for End-To-End Latency in Semi-Harmonic Task Systems

### 2024-09-25 paper.tex
structure

@@

@@

\section{Main Topic}

@@

>>>>

	State of the art: Release all tasks at the same time

	- Related work: Alessandro ECRTS

@@

\section{Motivating Example}

	Show that releasing all jobs at the same time is not optimal, and that you can get better results by manipulating phases.

@@

	What is the best phasing? Nobody has looked into that yet.

\section{Optimal Task Phasing for Harmonic Systems}

	Theorem: Phases need to be set at

	Proposition: How big is the gain that we get wrt synchronous?

\section{Optimal Task Phasing for Semi-Harmonic Systems}

	Look at task set with automotive periods 1,2,5,10,20,50,100,200,1000

	Thm: If all periods divide the largest period, the strategy from previous section still optimal phasing.

	If it does not divide, we need to make space bigger. We do that as follows \dots

	- immer wenn von größter Periode das erste mal zu nicht harmonischer Periode, um die Hälfte schieben

	Thm: Optimal phasing with this strategy for automotive periods.

	Proof: 
	- hyperperiod is at most twice as much, therefore at most two different partitioned job chains 
	- Length at least sum of all + phasings from each non harmonic task 
	- Can count number of times jumping from between non harmonic -> loosing at least one half every time

@@

	Apply our phasing in one or two real applications/ to workload based on real applications and report the gain.

	- ohne offset
	- random offset
	- unser offset

	- arbitrary phasing: use Matthias analysis (MRDA + one period)
